Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-28 manuscript/manuscript.Rmd
wording

In this regard, DRL provides a framework flexible enough to capture the intricate population dynamics that are relevant in fishery management.
Importantly, DRL is equipped with tools to deal with complex models for which simple policies might yield unsatisfactory results (and thus more refined techniques are needed to control them).
For example *long short-term memories (LSTMs)* may be used to incorporate not only $N_t$ but also $\mathrm{d}N_t/\mathrm{d}t$ into policy decisions---while this additional degree of freedom would make analytical control theory approaches unwieldy, it may be easily and cost-effectively implemented in DRL.
Similarly, *curriculum learning* [@curriculum-learning] or *open-ended learning* [@open-ended] could be incorporated to deal with phenomena such as parametric noise, parametric drift, and, more generally, for deriving generally well-performing agents *vis-à-vis* uncertainties in the system's dynamics. <!-- ML: Could also use LSTMs for parametric drift. Might be better to use a different selling point for curriculum learning like if you want to have a bit more generalizability in your RL agent. -->

>>>>

In this regard, DRL provides a framework flexible enough to capture the intricate population dynamics that are relevant in fishery management.
Importantly, DRL is equipped with tools to deal with complex models for which simple policies might yield unsatisfactory results (and thus more refined techniques are needed to control them).
For example, tools such as *long short-term memories* [@lstm], *curriculum learning* [@curriculum-learning] and *open-ended learning* [@open-ended] can be incorporated when faced with parametric noise or drift, or generally uncertainties about the agent's environment. 
These techniques can be used to obtain agents who perform well over a variety of different environments [@open-ended]. <!-- ML: Could also use LSTMs for parametric drift. Might be better to use a different selling point for curriculum learning like if you want to have a bit more generalizability in your RL agent. -->
